The Milky Way bar does not have to be slowing down

### 2022-04-04 paper/old/ms-old.tex
Add old folder to paper

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Star Bar]{On Star Formation at Dynamical Resonances of the Bar}

@@

% Abstract of the paper
\begin{abstract}
Long-term, secular processes can be important drivers of present-day galactic
properties. The Milky Way is known to host one and perhaps multiple bars whose
gravitational influence has observable consequences on both stellar and
gaseous components. It has long been known that along the major axis of a bar
gas can be driven towards the galactic center, fueling, e.g., the Central
Molecular Zone and nuclear activity. On the other hand, stars are known to
congregate near Lagrange points (i.e., minimums in the galactic potential),
forming known moving groups such as Hercules. We report the results of
isolated simulations incorporating both a state-of-the-art star formation and
feedback model (in which a multi-phase interstellar medium is generated
self-consistently) and a model of the Milky Way which forms a strong bar with
a pattern speed matched to current observations. We are able to show, for the
first time, that an enhancement of star formation may occur at the Lagrange
points. We derive a collisional analogue of the theory of dynamical resonances
and
\end{abstract}

@@

We convert a fraction (10\%) of the initial stellar disk of GALAKOS to a gas
disk. As described in \citet{2005MNRAS.361..776S}, the gas disk is initially
in hydrostatic equilibrium. We assumed an ideal EOS for the gas phase,
consistent with our underlying physical model. We make two further
modifications to this setup. First, we ``core'' the gas profile -- instead of
assuming the gas surface density profile is exponential, we assume it is a
constant value within some radius $R_{\text{core}}$. Specifically,
\beq
\Sigma_{\text{gas}} = \Sigma_{0,\text{gas}} \times \begin{cases} 
      e^{-R_{\text{core}}/H} & R \leq R_{\text{core}} \\
      e^{-R/H} & R > R_{\text{core}}\text{,}
   \end{cases}
\eeq
where $H$ is the scale length of the disk and $\Sigma_{0,\text{gas}} =
\frac{M_{\text{gas}}}{2\pi H^2}$ is the central surface density. When
$R_{\text{core}}/H=1$ and $1.4$, $\sim10\%$ and $\sim20\%$ of the gas disk
mass is removed, respectively. This mass is not returned to another component
and is thus removed from the initial conditions entirely. However, since our
assumed gas fraction is $10\%$, this only represents a total reduction in the
disk mass by a few percent. The surface density profile of the stellar disk is
unchanged, though its velocity distribution is suitably altered.

The second modification we make is to treat the initial disk particles as star
particles. In, e.g., \citet{2019MNRAS.489.4233M} the initial disk is assumed
to be a purely collisionless component with no feedback contributions.
Instead, we assume the initial disk particles are star particles so they may
contribute gas through AGB channels. This requires assigning an age and
metallicity to each star particle. We randomly draw the age and metallicity of
each star according to the age-metallicity-radius relation of
\citet{2018ApJ...865...96F}. This ignores vertical variations which is
implemented in other models \citep[e.g.][]{2020arXiv200503646S}.

@@

As a result, it is necessary to include a source of fresh gas to resupply the
galaxy. We found this to be quite problematic because several such techniques
we explored would either weaken or completely destroy the bar. We found that
it was necessary to include a somewhat \textit{ad hoc} implementation of gas
accretion from the circumgalactic medium (CGM).

Our method is inspired by the picture of a ``galactic fountain flow''
\citep{2006MNRAS.366..449F, 2008MNRAS.386..935F}. In this picture, gas is
launched from the central region of a spiral galaxy before falling back onto
the disk at a larger radii. In these models, the gas has lower angular
momentum than the disk when it rejoins the disk due to {\bf drag interactions
with the hot corona.}

We therefore have implemented a method to include ``hoses'' into AREPO. These
hoses are circular regions of radius $R_h$ placed along the $x$-axis at $x=\pm
R$. At a fixed timestep $\delta t$ each hose will spawn a number $N$ of gas
particles. The spawned gas particles have a fixed mass, a uniform initial
temperature of $10^4 \K$, and a uniform metallicity chosen to be solar.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Bars slowing down]{The Milky Way bar does not have to be slowing down}

@@

% Abstract of the paper
\begin{abstract}
Most disk galaxies harbor a rotating bar-like stellar structure at their
centers, of varying strengths and sizes. It has long been expected that the
rate at which galactic bars rotate is slowing down over time due to resonant
interactions between the bar and the outer disk or dark matter halo. On the
other hand, the gravitational influence of the bar can drive gas to the center
of the galaxy, providing a source of angular momentum for the bar, allowing it
to speed up. Using state-of-the-art numerical simulations (which include a
resolved cold phase of the interstellar medium) of an isolated disk galaxy, we
show that the angular momentum increase from gas infall is enough to counter
the angular momentum loss to the outer disk and halo. This effect does not
occur in previous generations of feedback and ISM models which rely on wind
particles to model large-scale feedback.

Long-term, secular processes can be important drivers of present-day galactic
properties. The Milky Way is known to host one and perhaps multiple bars whose
gravitational influence has observable consequences on both stellar and
gaseous components. It has long been known that along the major axis of a bar
gas can be driven towards the galactic center, fueling, e.g., the Central
Molecular Zone and nuclear activity. On the other hand, stars are known to
congregate near Lagrange points (i.e., minimums in the galactic potential),
forming known moving groups such as Hercules. We report the results of
isolated simulations incorporating both a state-of-the-art star formation and
feedback model (in which a multi-phase interstellar medium is generated
self-consistently) and a model of the Milky Way which forms a strong bar with
a pattern speed matched to current observations. We are able to show, for the
first time, that an enhancement of star formation may occur at the Lagrange
points. We derive a collisional analogue of the theory of dynamical resonances
and
\end{abstract}

@@

Including the gas phase was more problematic.

@@
